Reduced Gromov--Witten theory of hypersurfaces in genus one

### 2019-03-13 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@

\subsection{Recursive description of the divisors: type $C^0$} It remains to consider the components $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ contained in the exceptional locus of
\begin{equation*} \VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
In this case the corresponding cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ is a ray in the subdivision of a larger-dimensional cone $\sigma \in \Sigma$, corresponding to a combinatorial type $\Delta$ which assigns degree zero to the circuit. The associated stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ has smaller dimension than $\Dcal$.

>>>>

\subsection{Recursive description of the divisors: type $C^0$}

@@
